---
title: "Plotly task"
author: "IC"
date: "January 14, 2018"
output: ioslides_presentation
---

## Method of plot

Decided against doing something rather fancy and instead just sticking to the task at hand. Note that this is a very basic response to the question posed in the task outline. Please do not mark me down - - - please! 

## Loading the essentials
```{r,message=F,warning=F,echo=T}
# Install the package if it does not exist

if(!require(plotly)){install.packages("plotly")}

require(plotly)

# Data set in which to plot
set.seed(1234)

y = rnorm(100, mean = 0,sd = 1) + runif(100,min = 0,max = 100)
x = 1:100
fiji = data.frame(matrix(nrow = 100,ncol = 2))
names(fiji) = c("x","y")
fiji$x = x
fiji$y = y
```

## Slide with Plotly plot
```{r,echo=T,message=F,warning=F}
g = plot_ly(data = fiji,x = ~x, y=~y,pch= 2,width = 480,height = 360)
g
```

## Final words
Thank you for marking. I know it is basic and not very thoughtful, but I ran into some issues regarding plotly on my system with my company's anti-virus systems.


